Simulate Cut Off

### 2022-06-14 simulate_cutoff.Rmd
added new variable

@@

@@

*Population*. The data was simulated using the `rnorm` function assuming a normal distribution for 30 rating scale type items rounded to two decimal places. The item means were simulated as $\mu$ = 4 points with a $\sigma$  of .25 points. The item $\sigma$s were simulated as 2 points with a low variability ($\sigma$ = .2), medium variability (.4), and high variability (.8). Each population was simulated with 1000 data points.

```{r}
## add room to vary as part of the equation

# mu <- rnorm(30, 4, .25)
# sigma1 <- rnorm(30, 2, .2)
# sigma2 <- rnorm(30, 2, .4)
# sigma3 <- rnorm(30, 2, .8)

mu <- rnorm(30, 847.48, 150)
sigma1 <- rnorm(30, 350, 100)
sigma2 <- rnorm(30, 350, 150)
sigma3 <- rnorm(30, 350, 200)

population1 <- data.frame(
  item = rep(1:30, 1000), 
  score = rnorm(1000*30, mean = mu, sd = sigma1)
  )

population2 <- data.frame(
  item = rep(1:30, 1000), 
  score = rnorm(1000*30, mean = mu, sd = sigma2)
  )

population3 <- data.frame(
  item = rep(1:30, 1000), 
  score = rnorm(1000*30, mean = mu, sd = sigma3)
  )

#evidence that they are simulated correctly
tapply(population1$score, population1$item, mean) # around 4
tapply(population1$score, population1$item, sd) # around 2
sd(tapply(population1$score, population1$item, sd)) # around .2

tapply(population2$score, population2$item, mean) # around 4
tapply(population2$score, population2$item, sd) # around 2
sd(tapply(population2$score, population2$item, sd)) # around .4

tapply(population3$score, population3$item, mean) # around 4
tapply(population3$score, population3$item, sd) # around 2
sd(tapply(population3$score, population3$item, sd)) # around .8
```

@@

```{r}
# create pilot samples from 20 to 100
samples1 <- samples2 <- samples3 <- list() 
sizes <- c(20, 25, 30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 80, 85, 90, 95, 100)
for (i in 1:length(sizes)){
  samples1[[i]] <- population1 %>% 
    group_by(item) %>% 
    slice_sample(n = sizes[i])

  samples2[[i]] <- population2 %>% 
    group_by(item) %>% 
    slice_sample(n = sizes[i])

  samples3[[i]] <- population3 %>% 
    group_by(item) %>% 
    slice_sample(n = sizes[i])
}
```

@@

```{r}
# calculate the SEs and the cutoff scores 
SES1 <- SES2 <- SES3 <- list()
cutoffs1 <- cutoffs2 <- cutoffs3 <- list()
for (i in 1:length(samples1)){
  SES1[[i]] <- tapply(samples1[[i]]$score,
                     samples1[[i]]$item,
                     function (x){ sd(x)/sqrt(length(x))})
  SES2[[i]] <- tapply(samples2[[i]]$score,
                   samples2[[i]]$item,
                   function (x){ sd(x)/sqrt(length(x))})
  SES3[[i]] <- tapply(samples3[[i]]$score,
                 samples3[[i]]$item,
                 function (x){ sd(x)/sqrt(length(x))})

  cutoffs1[[i]] <- quantile(SES1[[i]], probs = seq(0, .9, by = .1))
  cutoffs2[[i]] <- quantile(SES2[[i]], probs = seq(0, .9, by = .1))
  cutoffs3[[i]] <- quantile(SES3[[i]], probs = seq(0, .9, by = .1))
}
```

@@

In this section, we simulate what a researcher might do if they follow our suggested application of AIPE to sample size planning based on well measured items. Assuming each pilot sample represents a dataset a researcher has collected, we will simulate samples of 20 to 500 to determine what the new sample size suggestion would be. We assume that samples over 500 may be considered too large for many researchers who do not work in teams. The standard error of each item was calculated for each suggested sample size by pilot sample size by population type.

```{r}
# sequence of sample sizes to try
samplesize_values <- seq(20, 1000, 5)

@@

  # create a blank table for us to save the values in 
  sim_table1 <- matrix(NA, 
                      nrow = length(samplesize_values), 
                      ncol = 30)

@@

    # temp dataframe that samples and summarizes
    temp <- samples1[[i]] %>% 
      group_by(item) %>% 
      slice_sample(n = samplesize_values[q], replace = T) %>% 
      summarize(se = sd(score)/sqrt(length(score)))

    sim_table1[q, 1:30] <- temp$se
    sim_table1[q, 31] <- samplesize_values[q]

    temp <- samples2[[i]] %>% 
      group_by(item) %>% 
      slice_sample(n = samplesize_values[q], replace = T) %>% 
      summarize(se = sd(score)/sqrt(length(score)))

    sim_table2[q, 1:30] <- temp$se
    sim_table2[q, 31] <- samplesize_values[q]

    temp <- samples3[[i]] %>% 
      group_by(item) %>% 
      slice_sample(n = samplesize_values[q], replace = T) %>% 
      summarize(se = sd(score)/sqrt(length(score)))

    sim_table3[q, 1:30] <- temp$se
    sim_table3[q, 31] <- samplesize_values[q]

@@

  summary_list1[[i]] <- sampled_values1[[i]] %>% 
    pivot_longer(cols = -c(sample_size)) %>% 
    rename(item = name, se = value) %>% 
    group_by(sample_size) %>% 
    summarize(Percent_Below0 = sum(se <= cutoffs1[[i]][1])/30,
             Percent_Below10 = sum(se <= cutoffs1[[i]][2])/30,
             Percent_Below20 = sum(se <= cutoffs1[[i]][3])/30,
             Percent_Below30 = sum(se <= cutoffs1[[i]][4])/30,
             Percent_Below40 = sum(se <= cutoffs1[[i]][5])/30,
             Percent_Below50 = sum(se <= cutoffs1[[i]][6])/30, 
             Percent_Below60 = sum(se <= cutoffs1[[i]][7])/30, 
             Percent_Below70 = sum(se <= cutoffs1[[i]][8])/30, 
             Percent_Below80 = sum(se <= cutoffs1[[i]][9])/30, 
             Percent_Below90 = sum(se <= cutoffs1[[i]][10])/30) %>% 
    mutate(original_n = sizes[i])

  summary_list2[[i]] <- sampled_values2[[i]] %>% 
    pivot_longer(cols = -c(sample_size)) %>% 
    rename(item = name, se = value) %>% 
    group_by(sample_size) %>% 
    summarize(Percent_Below0 = sum(se <= cutoffs2[[i]][1])/30,
             Percent_Below10 = sum(se <= cutoffs2[[i]][2])/30,
             Percent_Below20 = sum(se <= cutoffs2[[i]][3])/30,
             Percent_Below30 = sum(se <= cutoffs2[[i]][4])/30,
             Percent_Below40 = sum(se <= cutoffs2[[i]][5])/30,
             Percent_Below50 = sum(se <= cutoffs2[[i]][6])/30, 
             Percent_Below60 = sum(se <= cutoffs2[[i]][7])/30, 
             Percent_Below70 = sum(se <= cutoffs2[[i]][8])/30, 
             Percent_Below80 = sum(se <= cutoffs2[[i]][9])/30, 
             Percent_Below90 = sum(se <= cutoffs2[[i]][10])/30) %>% 
    mutate(original_n = sizes[i])

  summary_list3[[i]] <- sampled_values3[[i]] %>% 
    pivot_longer(cols = -c(sample_size)) %>% 
    rename(item = name, se = value) %>% 
    group_by(sample_size) %>% 
    summarize(Percent_Below0 = sum(se <= cutoffs3[[i]][1])/30,
             Percent_Below10 = sum(se <= cutoffs3[[i]][2])/30,
             Percent_Below20 = sum(se <= cutoffs3[[i]][3])/30,
             Percent_Below30 = sum(se <= cutoffs3[[i]][4])/30,
             Percent_Below40 = sum(se <= cutoffs3[[i]][5])/30,
             Percent_Below50 = sum(se <= cutoffs3[[i]][6])/30, 
             Percent_Below60 = sum(se <= cutoffs3[[i]][7])/30, 
             Percent_Below70 = sum(se <= cutoffs3[[i]][8])/30, 
             Percent_Below80 = sum(se <= cutoffs3[[i]][9])/30, 
             Percent_Below90 = sum(se <= cutoffs3[[i]][10])/30) %>% 
    mutate(original_n = sizes[i])
}

summary_DF <- bind_rows(summary_list1, 
                        summary_list2, 
                        summary_list3)
summary_DF$source <- rep(c("low", "med", "high"), each = length(sampled_values1)*length(samplesize_values))
```

@@

```{r}
summary_long_80 <- summary_DF %>% 
  pivot_longer(cols = -c(sample_size, original_n, source)) %>% 
  filter(value >= .80) %>% 
  arrange(sample_size, original_n, source, name) %>% 
  group_by(original_n, name, source) %>% 
  slice_head(n = 1) %>% 
  mutate(power = 80)

summary_long_85 <- summary_DF %>% 
  pivot_longer(cols = -c(sample_size, original_n, source)) %>% 
  filter(value >= .85) %>% 
  arrange(sample_size, original_n, source, name) %>% 
  group_by(original_n, name, source) %>% 
  slice_head(n = 1) %>% 
  mutate(power = 85)

summary_long_90 <- summary_DF %>% 
  pivot_longer(cols = -c(sample_size, original_n, source)) %>% 
  filter(value >= .90) %>% 
  arrange(sample_size, original_n, source, name) %>% 
  group_by(original_n, name, source) %>% 
  slice_head(n = 1) %>% 
  mutate(power = 90)

summary_long_95 <- summary_DF %>% 
  pivot_longer(cols = -c(sample_size, original_n, source)) %>% 
  filter(value >= .95) %>% 
  arrange(sample_size, original_n, source, name) %>% 
  group_by(original_n, name, source) %>% 
  slice_head(n = 1) %>% 
  mutate(power = 95)

@@

summary_long$source <- factor(summary_long$source, 
                              levels = c("low", "med", "high"),
                              labels = c("Low", "Medium", "High"))
summary_long$sd_original <- .2
summary_long$sd_original[summary_long$source == "Medium"] <- .4
summary_long$sd_original[summary_long$source == "High"] <- .8
summary_long$name <- gsub("Percent_Below", "Decile ", summary_long$name)
```

@@

>>>>

More real introduction on power, current trends to AIPE, and why items are key.

@@

# Explain the Procedure

Notes forthcoming.

@@

*Population*. The data was simulated using the `rnorm` function assuming a normal distribution for 30 scale type items. Each population was simulated with 1000 data points. No items were rounded for this simulation.

First, the scale of the data was manipulated by creating three sets of scales. The first scale was mimicked after small rating scales (i.e., 1-7 type style) using a $\mu$ = 4 with a $\sigma$ = .25 around the mean to create item mean variability. The second scale included a larger potential distribution of scores with a $\mu$ = 50 ($\sigma$ = 10) imitating a 0-100 scale. Last, the final scale included a $\mu$ = 1000 ($\sigma$ = 150) simulating a study that may include response latency data in the milliseconds. While there are many potential scales, these three represent a large number of potential variables in the social sciences. As we are suggesting variances as a key factor for estimating sample sizes, the scale of the data is influential on the amount of *potential* variance. Smaller ranges of data (1-7) cannot necessarily have the same variance as larger ranges (0-100).

Next, item variance heterogeneity was included by manipulating the potential $\sigma$ for each individual item. For small scales, the $\sigma$ = 2 points with a variability of .2, .4, and .8 for low, medium, and high heterogeneity in the variances between items. For the medium scale of data, $\sigma$ = 20 with a variance of 4, 8, and 12. Last, for the large scale of data, $\sigma$ = 350 with a variance of 100, 150, and 200 for heterogeneity.

```{r echo = F}
# small potential variability overall, sort of 1-7ish scale
mu1 <- rnorm(30, 4, .25)
sigma1.1 <- rnorm(30, 2, .2)
sigma2.1 <- rnorm(30, 2, .4)
sigma3.1 <- rnorm(30, 2, .8)

# medium potential variability 0 to 100 scale
mu2 <- rnorm(30, 50, 10)
sigma1.2 <- rnorm(30, 20, 4)
sigma2.2 <- rnorm(30, 20, 8)
sigma3.2 <- rnorm(30, 20, 12)

# large potential variability in the 1000s scale

mu3 <- rnorm(30, 1000, 150)
sigma1.3 <- rnorm(30, 350, 100)
sigma2.3 <- rnorm(30, 350, 150)
sigma3.3 <- rnorm(30, 350, 200)

while(sum(sigma3.3 < 0) > 0){
  sigma3.3 <- rnorm(30, 350, 200)
}

population1 <- data.frame(
  item = rep(1:30, 1000*3),
  scale = rep(1:3, each = 1000*30),
  score = c(rnorm(1000*30, mean = mu1, sd = sigma1.1),
            rnorm(1000*30, mean = mu2, sd = sigma1.2),
            rnorm(1000*30, mean = mu3, sd = sigma1.3))
  )

population2 <- data.frame(
  item = rep(1:30, 1000*3),
  scale = rep(1:3, each = 1000*30),
  score = c(rnorm(1000*30, mean = mu1, sd = sigma2.1),
            rnorm(1000*30, mean = mu2, sd = sigma2.2),
            rnorm(1000*30, mean = mu3, sd = sigma2.3))
  )

population3 <- data.frame(
  item = rep(1:30, 1000*3),
  scale = rep(1:3, each = 1000*30),
  score = c(rnorm(1000*30, mean = mu1, sd = sigma3.1),
            rnorm(1000*30, mean = mu2, sd = sigma3.2),
            rnorm(1000*30, mean = mu3, sd = sigma3.3))
  )

#evidence that they are simulated correctly
tapply(population1$score, list(population1$item, 
                               population1$scale), mean)
tapply(population1$score, list(population1$item,
                               population1$scale), sd)

tapply(population2$score, list(population2$item, 
                               population2$scale), mean)
tapply(population2$score, list(population2$item,
                               population2$scale), sd)

tapply(population3$score, list(population3$item, 
                               population3$scale), mean)
tapply(population3$score, list(population3$item,
                               population3$scale), sd) 
```

@@

```{r}
# create pilot samples from 20 to 100
samples1 <- samples2 <- samples3 <- list() 
sizes <- c(20, 25, 30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 80, 85, 90, 95, 100)
for (i in 1:length(sizes)){
  samples1[[i]] <- population1 %>% 
    group_by(item, scale) %>% 
    slice_sample(n = sizes[i])

  samples2[[i]] <- population2 %>% 
    group_by(item, scale) %>% 
    slice_sample(n = sizes[i])

  samples3[[i]] <- population3 %>% 
    group_by(item, scale) %>% 
    slice_sample(n = sizes[i])
}
```

@@

```{r}
# calculate the SEs and the cutoff scores 
SES1 <- SES2 <- SES3 <- list()
cutoffs1 <- cutoffs2 <- cutoffs3 <- list()
for (i in 1:length(samples1)){
  SES1[[i]] <- tapply(samples1[[i]]$score,
                     list(samples1[[i]]$item,
                          samples1[[i]]$scale),
                     function (x){ sd(x)/sqrt(length(x))})
  SES2[[i]] <- tapply(samples2[[i]]$score,
                   list(samples2[[i]]$item,
                        samples2[[i]]$scale),
                   function (x){ sd(x)/sqrt(length(x))})
  SES3[[i]] <- tapply(samples3[[i]]$score,
                 list(samples2[[i]]$item,
                      samples2[[i]]$scale),
                 function (x){ sd(x)/sqrt(length(x))})

  cutoffs1[[i]] <- apply(as.data.frame(SES1[[i]]), 2, 
                         quantile, 
                         probs = seq(0, .9, by = .1))
  cutoffs2[[i]] <- apply(as.data.frame(SES2[[i]]), 2, 
                         quantile, 
                         probs = seq(0, .9, by = .1))
  cutoffs3[[i]] <- apply(as.data.frame(SES3[[i]]), 2, 
                         quantile, 
                         probs = seq(0, .9, by = .1))
}
```

@@

In this section, we simulate what a researcher might do if they follow our suggested application of AIPE to sample size planning based on well measured items. Assuming each pilot sample represents a dataset a researcher has collected, we will simulate samples of 20 to 500 to determine what the new sample size suggestion would be. We assume that samples over 500 may be considered too large for many researchers who do not work in teams or have participant funds. The standard error of each item was calculated for each suggested sample size by pilot sample size by population type.

```{r}
# sequence of sample sizes to try
samplesize_values <- seq(20, 500, 5)

@@

  # create a blank table for us to save the values in 
  sim_table1 <- matrix(NA, 
                      nrow = length(samplesize_values), 
                      ncol = 30*3)

@@

    # temp dataframe that samples and summarizes
    temp <- samples1[[i]] %>% 
      group_by(item, scale) %>% 
      slice_sample(n = samplesize_values[q], replace = T) %>% 
      summarize(se = sd(score)/sqrt(length(score)),
                .groups = "keep")

    sim_table1[q, 1:90] <- temp$se
    sim_table1[q, 91] <- samplesize_values[q]

    temp <- samples2[[i]] %>% 
      group_by(item, scale) %>% 
      slice_sample(n = samplesize_values[q], replace = T) %>% 
      summarize(se = sd(score)/sqrt(length(score)),
                .groups = "keep")

    sim_table2[q, 1:90] <- temp$se
    sim_table2[q, 91] <- samplesize_values[q]

    temp <- samples3[[i]] %>% 
      group_by(item, scale) %>% 
      slice_sample(n = samplesize_values[q], replace = T) %>% 
      summarize(se = sd(score)/sqrt(length(score)),
                .groups = "keep")

    sim_table3[q, 1:90] <- temp$se
    sim_table3[q, 91] <- samplesize_values[q]

@@

  # summary list 1 ----
  summary_list1[[i]] <- sampled_values1[[i]] %>% 
    pivot_longer(cols = -c(sample_size)) %>% 
    rename(item = name, se = value) %>% 
    mutate(scale = rep(1:3, 30*length(samplesize_values))) %>% 
    mutate(item = rep(rep(1:30, each = 3), length(samplesize_values)))

  # cut offs for 1
  temp1.1 <- summary_list1[[i]] %>% 
    filter(scale == "1") %>% 
    group_by(sample_size, scale) %>% 
    summarize(Percent_Below0 = sum(se <= cutoffs1[[i]][1, 1])/30,
           Percent_Below10 = sum(se <= cutoffs1[[i]][2, 1])/30,
           Percent_Below20 = sum(se <= cutoffs1[[i]][3, 1])/30,
           Percent_Below30 = sum(se <= cutoffs1[[i]][4, 1])/30,
           Percent_Below40 = sum(se <= cutoffs1[[i]][5, 1])/30,
           Percent_Below50 = sum(se <= cutoffs1[[i]][6, 1])/30, 
           Percent_Below60 = sum(se <= cutoffs1[[i]][7, 1])/30, 
           Percent_Below70 = sum(se <= cutoffs1[[i]][8, 1])/30, 
           Percent_Below80 = sum(se <= cutoffs1[[i]][9, 1])/30, 
           Percent_Below90 = sum(se <= cutoffs1[[i]][10, 1])/30, 
           .groups = "keep") %>% 
    mutate(original_n = sizes[i], 
           source = "low")

  temp1.2 <- summary_list1[[i]] %>% 
    filter(scale == "2") %>% 
    group_by(sample_size, scale) %>% 
    summarize(Percent_Below0 = sum(se <= cutoffs1[[i]][1, 2])/30,
           Percent_Below10 = sum(se <= cutoffs1[[i]][2, 2])/30,
           Percent_Below20 = sum(se <= cutoffs1[[i]][3, 2])/30,
           Percent_Below30 = sum(se <= cutoffs1[[i]][4, 2])/30,
           Percent_Below40 = sum(se <= cutoffs1[[i]][5, 2])/30,
           Percent_Below50 = sum(se <= cutoffs1[[i]][6, 2])/30, 
           Percent_Below60 = sum(se <= cutoffs1[[i]][7, 2])/30, 
           Percent_Below70 = sum(se <= cutoffs1[[i]][8, 2])/30, 
           Percent_Below80 = sum(se <= cutoffs1[[i]][9, 2])/30, 
           Percent_Below90 = sum(se <= cutoffs1[[i]][10, 2])/30, 
           .groups = "keep") %>% 
    mutate(original_n = sizes[i],
           source = "low")

  temp1.3 <- summary_list1[[i]] %>% 
    filter(scale == "3") %>% 
    group_by(sample_size, scale) %>% 
    summarize(Percent_Below0 = sum(se <= cutoffs1[[i]][1, 3])/30,
           Percent_Below10 = sum(se <= cutoffs1[[i]][2, 3])/30,
           Percent_Below20 = sum(se <= cutoffs1[[i]][3, 3])/30,
           Percent_Below30 = sum(se <= cutoffs1[[i]][4, 3])/30,
           Percent_Below40 = sum(se <= cutoffs1[[i]][5, 3])/30,
           Percent_Below50 = sum(se <= cutoffs1[[i]][6, 3])/30, 
           Percent_Below60 = sum(se <= cutoffs1[[i]][7, 3])/30, 
           Percent_Below70 = sum(se <= cutoffs1[[i]][8, 3])/30, 
           Percent_Below80 = sum(se <= cutoffs1[[i]][9, 3])/30, 
           Percent_Below90 = sum(se <= cutoffs1[[i]][10, 3])/30, 
           .groups = "keep") %>% 
    mutate(original_n = sizes[i], 
           source = "low")

  #rejoin 
  summary_list1[[i]] <- bind_rows(temp1.1, temp1.2, temp1.3)

  # summary list 2 ----
  summary_list2[[i]] <- sampled_values2[[i]] %>% 
    pivot_longer(cols = -c(sample_size)) %>% 
    rename(item = name, se = value) %>% 
    mutate(scale = rep(1:3, 30*length(samplesize_values))) %>% 
    mutate(item = rep(rep(1:30, each = 3), length(samplesize_values)))

  # cut offs for 2
  temp2.1 <- summary_list2[[i]] %>% 
    filter(scale == "1") %>% 
    group_by(sample_size, scale) %>% 
    summarize(Percent_Below0 = sum(se <= cutoffs2[[i]][1, 1])/30,
           Percent_Below10 = sum(se <= cutoffs2[[i]][2, 1])/30,
           Percent_Below20 = sum(se <= cutoffs2[[i]][3, 1])/30,
           Percent_Below30 = sum(se <= cutoffs2[[i]][4, 1])/30,
           Percent_Below40 = sum(se <= cutoffs2[[i]][5, 1])/30,
           Percent_Below50 = sum(se <= cutoffs2[[i]][6, 1])/30, 
           Percent_Below60 = sum(se <= cutoffs2[[i]][7, 1])/30, 
           Percent_Below70 = sum(se <= cutoffs2[[i]][8, 1])/30, 
           Percent_Below80 = sum(se <= cutoffs2[[i]][9, 1])/30, 
           Percent_Below90 = sum(se <= cutoffs2[[i]][10, 1])/30, 
           .groups = "keep") %>% 
    mutate(original_n = sizes[i],
           source = "med")

  temp2.2 <- summary_list2[[i]] %>% 
    filter(scale == "2") %>% 
    group_by(sample_size, scale) %>% 
    summarize(Percent_Below0 = sum(se <= cutoffs2[[i]][1, 2])/30,
           Percent_Below10 = sum(se <= cutoffs2[[i]][2, 2])/30,
           Percent_Below20 = sum(se <= cutoffs2[[i]][3, 2])/30,
           Percent_Below30 = sum(se <= cutoffs2[[i]][4, 2])/30,
           Percent_Below40 = sum(se <= cutoffs2[[i]][5, 2])/30,
           Percent_Below50 = sum(se <= cutoffs2[[i]][6, 2])/30, 
           Percent_Below60 = sum(se <= cutoffs2[[i]][7, 2])/30, 
           Percent_Below70 = sum(se <= cutoffs2[[i]][8, 2])/30, 
           Percent_Below80 = sum(se <= cutoffs2[[i]][9, 2])/30, 
           Percent_Below90 = sum(se <= cutoffs2[[i]][10, 2])/30, 
           .groups = "keep") %>% 
    mutate(original_n = sizes[i], 
           source = "med")

  temp2.3 <- summary_list2[[i]] %>% 
    filter(scale == "3") %>% 
    group_by(sample_size, scale) %>% 
    summarize(Percent_Below0 = sum(se <= cutoffs2[[i]][1, 3])/30,
           Percent_Below10 = sum(se <= cutoffs2[[i]][2, 3])/30,
           Percent_Below20 = sum(se <= cutoffs2[[i]][3, 3])/30,
           Percent_Below30 = sum(se <= cutoffs2[[i]][4, 3])/30,
           Percent_Below40 = sum(se <= cutoffs2[[i]][5, 3])/30,
           Percent_Below50 = sum(se <= cutoffs2[[i]][6, 3])/30, 
           Percent_Below60 = sum(se <= cutoffs2[[i]][7, 3])/30, 
           Percent_Below70 = sum(se <= cutoffs2[[i]][8, 3])/30, 
           Percent_Below80 = sum(se <= cutoffs2[[i]][9, 3])/30, 
           Percent_Below90 = sum(se <= cutoffs2[[i]][10, 3])/30, 
           .groups = "keep") %>% 
    mutate(original_n = sizes[i],
           source = "med")

  #rejoin 
  summary_list2[[i]] <- bind_rows(temp2.1, temp2.2, temp2.3)

  # summary list 3 ----
  summary_list3[[i]] <- sampled_values3[[i]] %>% 
    pivot_longer(cols = -c(sample_size)) %>% 
    rename(item = name, se = value) %>% 
    mutate(scale = rep(1:3, 30*length(samplesize_values))) %>% 
    mutate(item = rep(rep(1:30, each = 3), length(samplesize_values)))

  # cut offs for 3 
  temp3.1 <- summary_list3[[i]] %>% 
    filter(scale == "1") %>% 
    group_by(sample_size, scale) %>% 
    summarize(Percent_Below0 = sum(se <= cutoffs3[[i]][1, 1])/30,
           Percent_Below10 = sum(se <= cutoffs3[[i]][2, 1])/30,
           Percent_Below20 = sum(se <= cutoffs3[[i]][3, 1])/30,
           Percent_Below30 = sum(se <= cutoffs3[[i]][4, 1])/30,
           Percent_Below40 = sum(se <= cutoffs3[[i]][5, 1])/30,
           Percent_Below50 = sum(se <= cutoffs3[[i]][6, 1])/30, 
           Percent_Below60 = sum(se <= cutoffs3[[i]][7, 1])/30, 
           Percent_Below70 = sum(se <= cutoffs3[[i]][8, 1])/30, 
           Percent_Below80 = sum(se <= cutoffs3[[i]][9, 1])/30, 
           Percent_Below90 = sum(se <= cutoffs3[[i]][10, 1])/30, 
           .groups = "keep") %>% 
    mutate(original_n = sizes[i],
           source = "high")

  temp3.2 <- summary_list3[[i]] %>% 
    filter(scale == "2") %>% 
    group_by(sample_size, scale) %>% 
    summarize(Percent_Below0 = sum(se <= cutoffs3[[i]][1, 2])/30,
           Percent_Below10 = sum(se <= cutoffs3[[i]][2, 2])/30,
           Percent_Below20 = sum(se <= cutoffs3[[i]][3, 2])/30,
           Percent_Below30 = sum(se <= cutoffs3[[i]][4, 2])/30,
           Percent_Below40 = sum(se <= cutoffs3[[i]][5, 2])/30,
           Percent_Below50 = sum(se <= cutoffs3[[i]][6, 2])/30, 
           Percent_Below60 = sum(se <= cutoffs3[[i]][7, 2])/30, 
           Percent_Below70 = sum(se <= cutoffs3[[i]][8, 2])/30, 
           Percent_Below80 = sum(se <= cutoffs3[[i]][9, 2])/30, 
           Percent_Below90 = sum(se <= cutoffs3[[i]][10, 2])/30, 
           .groups = "keep") %>% 
    mutate(original_n = sizes[i],
           source = "high")

  temp3.3 <- summary_list3[[i]] %>% 
    filter(scale == "3") %>% 
    group_by(sample_size, scale) %>% 
    summarize(Percent_Below0 = sum(se <= cutoffs3[[i]][1, 3])/30,
           Percent_Below10 = sum(se <= cutoffs3[[i]][2, 3])/30,
           Percent_Below20 = sum(se <= cutoffs3[[i]][3, 3])/30,
           Percent_Below30 = sum(se <= cutoffs3[[i]][4, 3])/30,
           Percent_Below40 = sum(se <= cutoffs3[[i]][5, 3])/30,
           Percent_Below50 = sum(se <= cutoffs3[[i]][6, 3])/30, 
           Percent_Below60 = sum(se <= cutoffs3[[i]][7, 3])/30, 
           Percent_Below70 = sum(se <= cutoffs3[[i]][8, 3])/30, 
           Percent_Below80 = sum(se <= cutoffs3[[i]][9, 3])/30, 
           Percent_Below90 = sum(se <= cutoffs3[[i]][10, 3])/30, 
           .groups = "keep") %>% 
    mutate(original_n = sizes[i],
           source = "high")

  #rejoin 
  summary_list3[[i]] <- bind_rows(temp3.1, temp3.2, temp3.3)

  }

summary_DF <- bind_rows(summary_list1, 
                        summary_list2, 
                        summary_list3)
```

@@

```{r}
summary_long_80 <- summary_DF %>% 
  pivot_longer(cols = -c(sample_size, original_n, source, scale)) %>% 
  filter(value >= .80) %>% 
  arrange(sample_size, original_n, source, scale, name) %>% 
  group_by(original_n, name, source, scale) %>% 
  slice_head(n = 1) %>% 
  mutate(power = 80)

summary_long_85 <- summary_DF %>% 
  pivot_longer(cols = -c(sample_size, original_n, source, scale)) %>% 
  filter(value >= .85) %>% 
  arrange(sample_size, original_n, source, scale, name) %>% 
  group_by(original_n, name, source, scale) %>% 
  slice_head(n = 1) %>% 
  mutate(power = 85)

summary_long_90 <- summary_DF %>% 
  pivot_longer(cols = -c(sample_size, original_n, source, scale)) %>% 
  filter(value >= .90) %>% 
  arrange(sample_size, original_n, source, scale, name) %>% 
  group_by(original_n, name, source, scale) %>% 
  slice_head(n = 1) %>% 
  mutate(power = 90)

summary_long_95 <- summary_DF %>% 
  pivot_longer(cols = -c(sample_size, original_n, source, scale)) %>% 
  filter(value >= .95) %>% 
  arrange(sample_size, original_n, source, scale, name) %>% 
  group_by(original_n, name, source, scale) %>% 
  slice_head(n = 1) %>% 
  mutate(power = 95)

@@

summary_long$source <- factor(summary_long$source, 
                              levels = c("low", "med", "high"),
                              labels = c("Low", "Medium", "High"))

summary_long$sd_original <- .2
summary_long$sd_original[summary_long$source == "Medium" &
                           summary_long$scale == "1"] <- .4
summary_long$sd_original[summary_long$source == "High" &
                           summary_long$source == "1"] <- .8

summary_long$sd_original[summary_long$source == "Low" &
                           summary_long$scale == "2"] <- 4
summary_long$sd_original[summary_long$source == "Medium" &
                           summary_long$scale == "2"] <- 8
summary_long$sd_original[summary_long$source == "High" &
                           summary_long$source == "2"] <- 12

summary_long$sd_original[summary_long$source == "Low" &
                           summary_long$scale == "3"] <- 100
summary_long$sd_original[summary_long$source == "Medium" &
                           summary_long$scale == "3"] <- 150
summary_long$sd_original[summary_long$source == "High" &
                           summary_long$source == "3"] <- 200

summary_long$name <- gsub("Percent_Below", "Decile ", summary_long$name)
```

@@

user_model4 <- lm(new_sample ~ sample_size + sd_original + original_n + scale, data = summary_long)
user_print4 <- apa_print(user_model4)
